A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-04 doc/large_strain.tex
change title and finite-strain

\begin{frontmatter}
  \title{
  Large-strain matrix-free finite element solver of hyperelastic problems with geometric multigrid preconditioner
  }

@@

    In this work we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the large-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts on the representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}

>>>>

\begin{frontmatter}
  \title{
  A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid
  }

@@

    In this work we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the finite-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts on the representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}
